---
title: "Walkthrough"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(openwashdata)
```


```{r basic, eval=FALSE}
library(openwashdata)
init_data_pkg("superheros",
              path = "openwashdata-dev")

```

Let's assume we have created a dataset named `superheros` in a folder `openwashdata-dev`.
This will open up new instance of RStudio with a project called superheros located in the `openwashdata-dev` folder. Let's focus our attention to this new instance of RStudio and walk through the steps in `bootstrap/bootstrap_pkg.R`.

## 1. Adding Authors

Once we got a the package skeleton, let's use the `authors.csv` template file to conveniently add multiple authors.


```
first_name,last_name,email,role,orcid
"Matt", "Bannert", "my@email.com", "aut","0000-0001-7901-9254"
"Lars", "Schöbitz", "another@email.com", "aut;cre","0000-0003-2196-5015"

```

>Note the use of ";" to list Lars' multiple roles as he is author and maintainer of the package.

## 2. Create a Citation File

Citation files facilitate citation of the data package as they are shown in multiple places such GitHub or Zenodo. To do so, simply run `use_cff()` as blue printed in the bootstrap file^[for more information on citation files and further modification, check the cffr package: https://docs.ropensci.org/cffr/]. 





In addition, citation information will be accessible through the corresponding R function which will create BibTeX output.


```{r}
library(superheros)
citation("superheros")

```

## 3. Extract Dictionary Skeleton from Data File 

Now let's move our raw data file(s) to the `data-raw` folder of our package.





## 4. Init Git Version Control 

Once a first version of all files is around, it's a good time to initialize a `git` repository^[Note that git is not part of R and a git client needs to be installed. For more information on git and git based workflows, see also https://rse-book.github.io/version-control.html.].

```{r,eval=FALSE}
init_git()
```












