---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgname

<!-- badges: start -->

[![License: CC BY
4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

<!-- badges: end -->

The goal of `pkgname` is to ...

## Installation

You can install the development version of pkgname from
[GitHub](https://github.com/pkgname) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/pkgname")
```

Alternatively, you can download the individual datasets as CSV or XLSX
file from the table below.

| dataset       | CSV                                                                                                    | XLSX                                                                                                     |
|--------------|-----------------------------|-----------------------------|
| dataname      | [Download CSV]()      | [Download XLSX]()      |

# Introduction




# Data

The package provides access to XX datasets ...

```{r}
library(pkgname)
```

```
The `pkgname` data set has {ncol(pkgname)} variables and {nrow(pkgname)} observations. For an overview of the variable names, see the following table.  
```

```{r, eval=FALSE}
pkgname
```

```{r, echo=FALSE}
readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::filter(file_name == "") |>  ##TODO: FILL ME
  dplyr::select(variable_name:description) |> 
  knitr::kable()
```

## Example
Write a demo snippet here.

```{r}

```

# License 
Data are available as [CC-BY](https://github.com/openwashdata/pkgname/blob/main/LICENSE.md).

# Citation
```{r}
citation()
```

## Related References


